# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
unzip("activity.zip")

activityDF <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

Make a histogram of the total number of steps taken each day
```{r}
stepsPerDay <- aggregate(steps ~ date, data = activityDF, FUN=sum)

hist(stepsPerDay$steps, breaks = nrow(stepsPerDay),
     main = "", xlab = "Steps Per Day", ylab = "Frequency", col = "lightblue")
```

Calculate and report the mean and median total number of steps taken per day
```{r}
meanStepsPerDay <- mean(stepsPerDay$steps)
medianStepsPerDay <- median(stepsPerDay$steps)
```

Mean number of steps taken per day: `r format(meanStepsPerDay, scientific = F)`

Median number of steps taken per day: `r medianStepsPerDay`

## What is the average daily activity pattern?

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
avg5Min <- aggregate(steps ~ interval, data = activityDF, FUN = mean)

plot(avg5Min, type = "l", xlab = "Intervals", ylab = "Steps")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
maxInterval <- avg5Min[which.max(avg5Min$steps), "interval"]
```

Interval with the maximum number of steps: `r maxInterval`

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
